---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BasicStatsByC

<!-- badges: start -->
<!-- badges: end -->

BasicStatsByc provides basic functions for statistical analysis and Bayesian statistics, including summary statistics, t-tests, chi-square tests, linear regression, Bayesian t-tests, Bayesian linear regression, and Bayesian correlation. A few of those functions comes with a (optional) plot. 

## Installation

You can install the development version of BasicStatsByC like so:

``` r
install.packages("devtools")

# Install BasicStatsByC from GitHub
devtools::install_github("Reiskorn03/BasicStatsByC")
```

## Example

Here, all functions in the BasicStatsByC package are listed in an example usage using the **mtcars** dataset.

Example usage summary_stats: 

```{r example summary_stats}
library(BasicStatsByC)

# Compute summary statistics for the mtcars dataset
summary_stats(mtcars)

```

Example usage t_test: 

```{r example t-test}
# Perform a t-test comparing mpg between automatic and manual transmissions
t_test(mtcars, "am", "mpg")
```

Example usage chi_square_test:

```{r example chi-square test}
# Perform a chi-square test between the number of cylinders and the number of gears
chi_square_test(mtcars, "cyl", "gear")
```

Example usage simple_lm: 

```{r example lr}
# Fit a linear regression model of mpg on weight
simple_lm(mtcars, mpg ~ wt)
```

Example usage bayesian_t_test: 

```{r example Bayesian t-test}
# Perform a Bayesian t-test comparing mpg between automatic and manual transmissions
bayesian_t_test(mtcars, "am", "mpg")
```

Example usage bayesian_lm: 

```{r Bayesian linear regression model}
# Fit a Bayesian linear regression model of mpg on weight
bayesian_lm(mtcars, mpg ~ wt)
```

Example usage bayesian_correlation:

```{r Bayesian correlation}
# Compute Bayesian correlation between mpg and weight
bayesian_correlation(mtcars, "mpg", "wt")
```
